Tropical Andes plant checklist using GIFT

### 2023-10-31 code/L0/L0_TropicalAndes_plants_checklist.Rmd
add genus based on taxon_id from checklist

```{r}
checklist <- GIFT_checklists(taxon_name = "Angiospermae", taxonomic_group = TRUE, floristic_group = "all", shp = TropicalAndes_IUCNHabitat_Forest, overlap = "extent_intersect")
```

>>>>

```{r}
checklist <- GIFT_checklists(taxon_name = "Angiospermae", taxonomic_group = TRUE, floristic_group = "all", shp = TropicalAndes_IUCNHabitat_Forest, overlap = "extent_intersect")
```
```{r}
glimpse(checklist$checklists)
```
```{r}
#add genus based on work_ID
full <- GIFT_taxonomy()
```

```{r}
genus_ID <- checklist$checklists$genus_ID
genus_list <- full %>% filter(taxon_ID %in% genus_ID) %>% select(taxon_ID, taxon_name)
names(genus_list) <- c("genus_ID", "genus")
```

```{r}
checklist_tax <- dplyr::inner_join(checklist$checklists, genus_list)
```

```{r}
print("The number of species is")
length(unique(checklist_tax$work_species))
print("The number of genera is")
length(unique(checklist_tax$genus))
print("The number of families is")
length(unique(checklist_tax$family))
```

# Write data to csv
```{r}
write.csv(checklist_tax, file = file.path(output_path,"TropicalAndes_plant_checklist.csv"))
```
